The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2024-05-24 OA.tex
revisions for r3
new submission

We now present analysis of the extent to which the survey-responding sample is representative and balanced.
Table \ref{SS_cond_survet} presents information about survey non-response.
Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex. 
As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
In exercises that rely on a single survey question, we use data for every borrower who answered that question.
In the random forest exercises described below, we use data for every borrower who answered at least one survey question.

@@

\begin{table}[H]
\caption{Balance conditional on survey response and question-by-question response rates} %by treatment arm}
\label{SS_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/SS_cond_survey.tex}}
\end{center}
\scriptsize

@@

\begin{landscape}
\begin{table}[H]
\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
\label{TUT_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/tut_cond_survey.tex}}
\end{center}
\scriptsize

>>>>

We now present analysis of the extent to which the survey-responding sample is representative and balanced.
Table \ref{SS_cond_survey} presents information about survey non-response.
Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
Table \ref{TUT_cond_survey} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex. 
As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
In exercises that rely on a single survey question, we use data for every borrower who answered that question.
In the random forest exercises described below, we use data for every borrower who answered at least one survey question.

@@

\begin{table}[H]
\caption{Balance conditional on survey response and question-by-question response rates} %by treatment arm}
\label{SS_cond_survey}
\begin{center}
\scriptsize{\input{./Tables/SS_cond_survey.tex}}
\end{center}
\scriptsize

@@

\begin{landscape}
\begin{table}[H]
\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
\label{TUT_cond_survey}
\begin{center}
\scriptsize{\input{./Tables/tut_cond_survey.tex}}
\end{center}
\scriptsize
